---
title: "DaparViz User manual"
author: 
- name: Samuel Wieczorek
- name: Thomas Burger
package: DaparViz
abstract: >
    The package DaparViz is a R package which provides functions to vizualize quantitative data from label-free proteomics experiments. It can deal with several data formats such as MSnSet, QFeatures or event simple lists. This document covers the functionalities available in `r BiocStyle::pkg_ver('DaparViz')`.
date: "`r Sys.Date()`"
output:
    BiocStyle::html_document:
        highlight: tango
        number_sections: yes
        toc: true
        toc_depth: 2
vignette: >
    %\VignetteIndexEntry{DaparViz User Manual}
    %\VignetteEngine{knitr::rmarkdown}
    %%\VignetteKeywords{Softmware, Mass Spectrometry, Quantitative }
    %\VignetteEncoding{UTF-8}
---

\newcommand{\shellcmd}[1]{\\\indent\indent\texttt{\footnotesize\# #1}}

\newcommand{\Rcmd}[1]{\\\indent\indent\texttt{\footnotesize\# #1}}

\newcommand{\bordurefigure}[1]{\fbox{\includegraphics{#1}}}

```{r echo=FALSE}
BiocStyle::markdown()
```

# Introduction

\section{Installation}\label{sec:install}

The `DaparViz` package is a Shiny app which provides a series of plots dedicated to the analysis of proteomics data. It can 
deal with two data structures: `MSnSet` and `QFeatures`.

It has been developped as a Shiny module so as to be flexible: it can run standalone- or can be inserted in another Shiny app.
In that sense, it can be used on its own; or as a complement to the numerous 
Bioconductor packages (\url{https://www.bioconductor.org/}) it is compliant with; or through the `Prostar` interface.

`Prostar` (Proteomics statistical analysis with R) is a 
web interface based on Shiny technology (\url{http://shiny.rstudio.com/}) that provides GUI (Graphical User Interfaces).
The experiment package `DaparToolshedData` contains many datasets that can be used as examples.
`DaparViz` contains built-in plots but have the capability to show plots developped by other developper (as a Shiny app).


\section{Installation}\label{sec:install}

To install this package, start R (version "4.3") and enter:

```
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("DaparViz")
```

For older versions of R, please refer to the appropriate Bioconductor release.



\section{Session information}\label{sec:sessionInfo}

```{r}
sessionInfo()
```
